Validation of Visual Statistical Inference, Applied to Linear Models

### 2013-04-12 paper_jasa.tex
re-worked conclusions

This paper has demonstrated that statistical graphics can be used in statistical inference and validates the lineup protocol proposed by \citet{buja:2009}. Specific terminology was defined, and methods for obtaining the $p$-value and estimating the power of visual tests were introduced. It was assumed that observers select the plot having the strongest signal in the lineup, in order to calculate the theoretical power,  and the experimental data proved to be consistent with this assumption.  The simulation study showed that  results obtained by visual inference are comparable to those obtained by conventional inference, in the setting where %conventional testing can be done. Visual inference is intended to provide valid tests where 
no conventional test exists, and our experiments in a controlled scenario suggest that it will perform as expected in the intended applications. The power of a visual test increases with the number of observers, which interestingly, leads to a result that the theoretical power of visual test can be better than that of conventional tests.

>>>>

This paper has demonstrated that statistical graphics can be used in statistical inference and validates the lineup protocol proposed by \citet{buja:2009}. Specific terminology was defined, and methods for obtaining the $p$-value and estimating the power of visual tests were introduced.  In order to calculate the theoretical power, it was assumed that observers will select the plot having the strongest signal in the lineup, and the experimental data suggests that for most observers this assumption holds.  Results from visual inference in the controlled setting of the simulation study are comparable to those obtained by conventional inference. %, in the setting where %conventional testing can be done. 
Visual inference is intended to provide valid tests where 
no conventional test exists, and our experiments in a controlled scenario suggest that it will perform as expected in the intended applications. The power of a visual test increases with the number of observers, which interestingly, leads to a result that the theoretical power of visual test can be better than that of conventional tests.
